{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-15 Notebook LaTEX/SAGD Under Interpolation/main.tex
;~;

% ==============================================================================

@@

    \textbf{Notations}. 

@@

    \subsection{Properties of functions, characterizations}
        The definitions are ordered from the weakest to strongest. 
        \begin{definition}[semi strongly convex function \textcolor{red}{NEW}]\label{def:semi-scnvx}
            A function $F: \RR^n \rightarrow \overline \RR$ is a semi strongly convex function, abbreviated as ``Semi-SCNVX'' with respective to a linear mapping $A \in \RR^{m \times n}$ if $F - \frac{1}{2}\Vert Ax\Vert^2$ is a convex function. 
            Any $\mu \ge 0$ strongly convex function is Semi-SCNVX with $A = \sqrt{\mu}I$. 
            But the converse is not true because a seminorm is not a norm. 
            One feature of a Semi-SCNVX function is that it doesn't have a unique minimizer which differs it from strong convexity. 
            It may not have a unique minimizer because it's not necessary that $\kernel A = \{\mathbf 0\}$. 

@@

        \begin{definition}[smooth Semi-SCNVX \textcolor{red}{NEW}]\label{def:seminorm-smooth-scnvx}
            Let $m, n\in \N$ be a natural numbers. 
            Let $f:\RR^m \rightarrow \RR$ be a differentiable function and full domain. 
            If there exists $A_1: \RR^{m\times n}$ and, $A_2 \in \RR^{m \times n}$ matrices such that it satisfies:

@@

                (\forall x \in \RR^m)(\forall y \in \RR^m)\;
                \frac{1}{2}\Vert A_1x - A_1y\Vert^2 \le 
                D_f(x, y) \le \frac{1}{2}\Vert A_2x - A_2y\Vert^2. 

@@

            Then, we call this function is semi-relative smooth with respect to $A_1$, and semi convex to $A_2$

@@

            The definition exchanged the $\Vert \cdot\Vert^2$ for a seminorm squared: $x \mapsto \Vert A_1x\Vert^2$ with some $A: \RR^m \rightarrow \RR^n$ for the definition of relative smoothness and relative strong convexity. 
            Obviously, it has $\Vert A_1x\Vert \le \Vert A_2x\Vert$ for all $x\in \RR^m$, which further implies that $\ker A_1\supseteq\ker A_2$. 
        \begin{theorem}[semi Jesen inequality \textcolor{red}{NEW}]\label{thm:semi-scnvx-equiv}
            A function $F$ is Semi-SNCVX with $A \in \RR^{m \times n}$ (Definition \ref{def:semi-scnvx}) if and only if, for all $x, y \in \RR^n$ and, $\lambda \in [0, 1]$ it satisfies the inequality: 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2. 
            For all $\lambda \in \RR, x \in \RR^n, y \in \RR^n$ it has $-1/2\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 = (1/2)(\lambda\Vert Ax\Vert^2 + (1 - \lambda)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\Vert Ax - Ay\Vert^2)$ by verifying: 
                & -\frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 + 
                    \frac{\lambda}{2}\Vert Ax\Vert^2 + \frac{1 - \lambda}{2}\Vert Ay\Vert^2 - \frac{\lambda(1 - \lambda)}{2}\Vert Ay - Ax\Vert^2
                -\frac{1}{2}\left(
                    \lambda^2\Vert Ax\Vert^2 + (1 - \lambda)^2\Vert Ay\Vert^2 - 2\lambda(1 - \lambda) \langle Ax, Ay\rangle
                    + 
                        \frac{\lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
                    \right)\Vert Ax\Vert^2 + \left(
                        \frac{1 - \lambda}{2} - \frac{\lambda(1 - \lambda)}{2}
                    \right)\Vert Ay\Vert^2 - \lambda(1 - \lambda)\langle Ay, Ax\rangle
                &= - \frac{\lambda^2}{2}\Vert Ax\Vert^2 - \frac{(1 - \lambda)^2}{2}\Vert Ay\Vert^2
                    + 
                        \frac{\lambda}{2} - \frac{\lambda - \lambda^2}{2}
                    \right)\Vert Ax\Vert^2 + \left(
                        \frac{1 - \lambda}{2} - \frac{\lambda - \lambda^2}{2}
                    \right)\Vert Ay\Vert^2
                &= 0
            Using the above result we can prove the equivalency because 
            {\small
                0 &\le F(\lambda x + (1 - \lambda)y) + \lambda F(x) + (1 - \lambda)F(y) -\frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2
                &=  F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
                + \lambda F(x) - \frac{\lambda}{2}\Vert Ax\Vert^2 
                + (1 - \lambda)F(y) - \frac{1 - \lambda}{2} \Vert Ay\Vert^2 
                    - \frac{\lambda(1 - \lambda)}{2} \Vert Ay - Ax\Vert^2 + \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2
                    + \frac{1}{2}\Vert Ax\Vert^2 + \frac{1}{2}\Vert Ay\Vert^2 
                F(\lambda x + (1 - \lambda)y) - \frac{1}{2}\Vert A(\lambda x + (1 - \lambda)y)\Vert^2 
                    + \lambda \left(F(x) - \frac{1}{2}\Vert Ax\Vert^2\right) 
                    + (1 - \lambda)\left(F(y) - \frac{1}{2} \Vert Ay\Vert^2\right). 
            }
            The last line shows that the function $F(x) - \frac{1}{2}\Vert Ax\Vert^2$ is convex, the chain of equality shows the equivalence. 

@@

        The following theorem classifies a class of semi strongly convex function. 

@@

        \begin{theorem}[affine composite smooth and strongly convex]\label{thm:aff-smooth-sq-scnvx}
            Let $f: \RR^n \rightarrow \RR$ be an $L$ smooth and, $\mu \ge 0$ strongly convex.
            Let $A: \RR^m \rightarrow \RR^n$, $b \in \RR^n$ be arbitrary and, define $h: \RR^m \rightarrow \RR= x \mapsto f(Ax - b)$. 
            Ddenote $\Pi = \Pi_{\ker A}$ to be the projection operator onto the kernel of $A$, denote $\Vert A\Vert$ to be the operator norm of the matrix, and $\sigma_{\min}(A)$ to be the smallest non-zero eigenvalues of $A$ in absolute value.
            Then, it satisfies for all $x \in \RR^m, y \in \RR^m$:  

@@

                \frac{\mu \sigma_{\min}(A)^2}{2}\Vert (I - \Pi)(x - y)\Vert^2
                \le \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
                \le D_h(x, y) \le \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 

@@

            Therefore, it satisfies Definition \ref{def:semi-scnvx} with $A_1 = \sqrt{L}A, A_2 = \sqrt{\mu}A$ so it's Semi-SCNVX. 

@@

            Then the Bregman divergence of $h$ is: 

@@

                D_h(x, y) &= h(x) - h(y) - \langle \nabla h(y), x - y\rangle
                &= f(Ax - b) - f(Ay - b) - \langle A^T\nabla f(Ay - b), x - y\rangle
                &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - Ay\rangle
                &= f(Ax - b) - f(Ay - b) - \langle \nabla f(Ay - b), Ax - b - (Ay - b)\rangle
                &= D_f(Ax - b, Ay - b). 
            Since $f$ is $L$ smooth and $\mu \ge 0$ strongly convex, it means 
                \frac{\mu}{2}\Vert Ax - Ay\Vert^2
                \frac{\mu}{2}\Vert Ax - b - (Ay - b)\Vert^2 
                &\le D_f(Ax - b, Ay - b)
                &= D_h(x, y) 
                &\le \frac{L}{2} \Vert Ax - Ay\Vert^2
                &\le \frac{L\Vert A\Vert^2}{2} \Vert x - y\Vert^2. 
            Using some linear algebra, one can represent $x - y$ as their orthogonal components in $\ker A$, $\ker A^T$ so it has 
                \frac{\mu}{2}\Vert A(x - y)\Vert^2 &= 
                \frac{\mu}{2}\Vert A(\Pi(x - y) + (1 - \Pi)(x - y))\Vert^2

@@

                \frac{\mu}{2}\Vert A(1 - \Pi)(x - y))\Vert^2

@@

                &\ge \frac{\mu\sigma_{\min}(A)}{2}\Vert (1 - \Pi)(x - y)\Vert^2. 

@@

            These results makes for the final inequalities: 

@@

                \frac{\mu\sigma_{\min}(A)}{2}\Vert (I - \Pi)(x - y)\Vert^2
                \le 
                D_h(x, y) \le 
                \frac{L\Vert A\Vert^2}{2}\Vert x - y\Vert^2. 

@@

        \begin{theorem}[affine minimizer set for aff comp smooth strongly convex]
            \todoinline{NOT FINISHED YET.}
    \subsection{Important inequalities}
            \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
                The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
                The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
                Let $F = f + g$ satisfies \ref{ass:smooth-plus-nonsmooth} and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
            \begin{assumption}[affine composite Semi-CNVX remative smooth plus non-smooth]\label{ass:snorm-smth-p-nsmth}
                Let $A \in \RR^{m\times n}, b \in \RR^n$
                Let $F(x): \RR^{m} \mapsto \overline\RR := x \mapsto f(x) + g(x)$. 
                Assume that: 
                \begin{enumerate}[noitemsep]
                    \item $f:\RR^m \rightarrow \RR := x \mapsto h(Ax - b)$ where $h:\RR^n\rightarrow \RR$ is $L$ Lipschitz smooth and, $\mu\ge 0$ strongly convex, then it satisfies Theorem \ref{thm:aff-smooth-sq-scnvx} with $L > \mu \ge 0$ and $A \in \RR^{m \times n}$. 
                    \item $g:\RR^m \mapsto \overline \RR$ is a convex, proper and closed function. 
                \end{enumerate}
            \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
                Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
                For any $x\in \RR^n$, define $x^+ = T_L(x)$. 
                Then, there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$ and, for all $z \in \RR^n$ it satisfies the inequality: 
                    0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                    &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                    - \frac{\mu}{2}\Vert z - x\Vert^2
                    - \frac{B}{2}\Vert x - x^+\Vert^2. 
                Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
                The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
                The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:snapg-v2} with line search routine to determine $L_k$. 
                Each of the reference books gives a proof of the theorem. 
                But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
            The following theorem attempts to generalize Theorem \ref{thm:pg-ineq}. 
            \begin{theorem}[proximal gradient inequality with semi-scnvx \textcolor{red}{NEW}]\label{thm:pg-ineq-semi-scnvx}
                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$. 
                For any $x \in \RR^n$, let $x^+ = T_B(x | F)$. 
                Let $\sigma_{\min}(A)$ denotes the minimum non-zero singular value of $A$ in absolute value. 
                Let $\Pi = \Pi_{\ker A}$ be the linear operator that project onto the kernel of $A$. 
                Then, there exists some $B \ge 0$ such that $D_f(x^+, x) \le \frac{B}{2}\Vert x - x^+\Vert^2$ and, for all $z \in \RR^m$ it satisfies the inequality: 
                    0 &\le F(z) - F(x^+) 
                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
                    + \frac{B}{2}\Vert z - x\Vert^2
                    - \frac{B}{2}\Vert z - x^+\Vert^2
                    &\le F(z) - F(x^+)
                    - \frac{B}{2}\Vert z - x^+\Vert^2 
                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x) \Vert^2
                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 
                Firstly, such a $B > 0$ exists, for example $B = L\Vert A\Vert^2$ would be an option because from Definition \ref{def:seminorm-smooth-scnvx}, it for all $x, y$, $D_f(x, y) \le L/2\Vert Ax - Ay \Vert^2 \le L/2\Vert A\Vert^2\Vert x - y\Vert^2$. 
                But it can be much smaller. 
                \par
                The function $z \mapsto g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2$ inside the proximal gradient operator has the minimizer $x^+$.  
                This function is also the sum of a convex, proper closed function $g$ and, a simple quadratic and, it's $B > 0$ strongly convex hence, it satisfies the quadratic growth conditions over its minimizer $x^+ = T_B(x|F)$ so, it follows that for all $z \in \RR^m$: 

@@

                    -\frac{B}{2}\Vert z - x^+\Vert^2 
                    + g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2

@@

                        - g(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2

@@

                    -\frac{B}{2}\Vert z - x^+\Vert^2 
                    + \left(g(z) + f(z) - f(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2\right)
                        +\left(- g(x^+) - f(x^+) + f(x^+) - f(x) - \langle \nabla f(x), x^+ - x\rangle - \frac{B}{2}\Vert x^+ - x\Vert^2\right)

@@

                    -\frac{B}{2}\Vert z - x^+\Vert^2 
                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
                        + \left(- F(x^+) + D_f(x^+, x) - \frac{B}{2}\Vert x^+ - x\Vert^2\right)

@@

                    &\underset{\text{(a)}}{\le }
                    -\frac{B}{2}\Vert z - x^+\Vert^2 
                    + \left(F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2\right)
                    - F(x^+)
                    - \frac{B}{2}\Vert z - x^+\Vert^2 
                    + F(z) - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
                    + \frac{B}{2}\Vert z - x\Vert^2
                    - F(x^+)
                    &= F(z) - F(x^+) 
                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
                    + \frac{B}{2}\Vert z - x\Vert^2
                    - \frac{B}{2}\Vert z - x^+\Vert^2. 
                At (a), we used the fact that line search asserted the condition $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$. 
                At (b) we applied results from Theorem \ref{thm:aff-smooth-sq-scnvx}. 
                Continuing it further with the results from \ref{thm:aff-smooth-sq-scnvx} it adds another inequality: 
                    0&\le  F(z) - F(x^+) 
                    - \frac{\mu}{2}\Vert Az - Ax\Vert^2 
                    + \frac{B}{2}\Vert z - x\Vert^2
                    - \frac{B}{2}\Vert z - x^+\Vert^2
                    &\le F(z) - F(x^+) 
                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                    + \frac{B}{2}\Vert z - x\Vert^2
                    - \frac{B}{2}\Vert z - x^+\Vert^2
                    &= F(z) - F(x^+) 
                    - \frac{\sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                        + \frac{B}{2}\Vert \Pi(z - x)\Vert^2
                        + \frac{B}{2}\Vert (I - \Pi)(z - x)\Vert^2
                        - \frac{B}{2}\Vert z - x^+\Vert^2
                    &= F(z) - F(x^+) 
                    - \frac{B}{2}\Vert z - x^+\Vert^2
                    + \frac{B - \sigma_{\min}(A)^2\mu}{2}\Vert (I - \Pi)(z - x)\Vert^2
                    + \frac{B}{2}\Vert \Pi(z - x)\Vert^2. 

@@

                When $\ker A = \{\mathbf 0\}$, this theorem is equivalent to Theorem \ref{thm:pg-ineq} but with $\mu$ being $\sigma_{\min}(A)$ instead. 

@@

            The following theorem attempts to generalize Theorem \ref{thm:semi-scnvx-equiv} for relatively smooth plus non-smooth function. 
            \begin{theorem}[seminorm smooth plus non-smooth Jensen \textcolor{red}{NEW}]\label{thm:smnrm-jnsn-smth-nsmth}
                Suppose that $F:\RR^m \rightarrow \overline \RR := x \mapsto f(x) + g(x)$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $L > \mu \ge 0$ and $A \in \RR^{m\times n}$.
                Let $\Pi = \Pi_{\ker A}$ be the projection onto the kernel of $A$. 
                Let $\sigma_{\min}(A)$ denote the smallest non-zero singular value of $A$ in absolute value. 
                Then, for all $x, y \in \RR^m$ and, $\lambda \in [0, 1]$ it satisfies the inequality: 

@@

                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\sigma_{\min}(A)^2\lambda(1 - \lambda)\mu}{2}\Vert (I - \Pi)(x - y)\Vert^2. 
                $f$ satisfies Definition \ref{def:seminorm-smooth-scnvx} with $L > \mu, A$, so for all $x, y \in \RR^m$ it has 
                    0 &\le D_f(x, y) - \frac{\mu}{2}\Vert Ax - Ay\Vert^2 
                    \le \frac{L - \mu}{2}\Vert Ax - Ay\Vert^2. 
                Using some algebra (or equivalent some properties of Bregman divergence), it shows that the function $f - \mu/2 \Vert A(\cdot)\Vert^2$ is a convex function, therefore, $f + g - \mu/2\Vert A(\cdot)\Vert^2 = F - \frac{\mu}{2}\Vert A(\cdot)\Vert^2 = F - \frac{1}{2}\Vert \sqrt{\mu}A(\cdot)\Vert^2$ is also a convex function. 
                Applying Theorem \ref{thm:semi-scnvx-equiv} it has for all $z, x \in \RR^m$ and, $\lambda \in [0, 1]$ the inequality: 
                    F(\lambda z + (1 - \lambda)y) &\le \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu}{2}\Vert Ax - Ay\Vert^2
                    &\le 
                    \lambda F(z) + (1 - \lambda)F(x) - \frac{\lambda(1 - \lambda)\mu\sigma_{\min}(A)^2}{2}\Vert (I - \Pi) x - y\Vert^2. 
                The second inequality uses Theorem \ref{thm:aff-smooth-sq-scnvx}. 

\section{Stochastic accelerated proximal gradient}
    First, this is an overview of this section.

    \begin{assumption}[sum of many affine composite]\label{ass:sum-of-many-aff-comp}
        Let $A^{(1)}, A^{(2)}, \ldots A^{(n)}$ be a list of $\RR^{m\times n}$ matrices and, $b^{(1)}, b^{(2)}, \ldots, b^{(n)}$ be a list of vectors in $\RR^n$. 
        Suppose $F:\RR^m \rightarrow \overline \RR:= \frac{1}{n}\sum_{i = 1}^{n} F_i(x)$, so it admits representations 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)}x - b^{(i)}) + g_i(x)
        \end{align*}
        Where, each $F_i = f_i + g_i$ satisfies Assumption \ref{ass:snorm-smth-p-nsmth} with $K^{(i)} > \nu^{(i)} \ge 0, b^{(i)} \in \RR^n$ and $A^{(i)} \in \RR^{m \times n}$. 
        So, each $h_i$ are $\nu^{(i)}$ strongly convex and $K^{(i)}$ Lipschitz smooth. 
        \par
        Take note that the function $f(x) = \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)})$ is the composition of the strongly convex function $h = \frac{1}{n}\sum_{i = 1}^{n} h_i$ that is a $\RR^{mn}\rightarrow \RR$ mapping with strong convexity $\frac{1}{n}\sum_{i = 1}^{n} \nu^{(i)}$ and, the affine $\RR^m \rightarrow \RR^{mn}$ mapping $\mathcal A := x \mapsto (A^{(1)}x - b^{(1)},\ldots,  A^{(n)}x - b^{(n)})$. 
        $f$ satisifes Theorem \ref{thm:aff-smooth-sq-scnvx} and it can be written as: 
        \begin{align*}
            f(x) = \sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) = h(\mathcal A x). 
        \end{align*}
    \end{assumption}

    \begin{assumption}[sum of many]\label{ass:sum-of-many}
        Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where each $F_i = f_i + g_i$, so it can be written as: 
        \begin{align*}
            F(x) = f(x) + g(x) = \frac{1}{n}\sum_{i = 1}^{n} f_i(x) + g_i(x)
        \end{align*}
        Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g_i:\RR^n \rightarrow \overline \RR$ is a closed convex proper function satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
        \par 
        Take note that, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}g_i$ therefore, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/n)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
    \end{assumption}
    Both assumptions are equivalent, functions satisfies one can be translated in form so it satisfies the other with some extra/fewer parameters. 
    However, it's important to know that for a $F := \frac{1}{n}\sum_{i = 1}^{n} h_i(A^{(i)} - b^{(i)}) + g_i(x)$ satisfying Assumption \ref{ass:sum-of-many-aff-comp}, Theorem \ref{thm:pg-ineq-semi-scnvx}, \ref{thm:smnrm-jnsn-smth-nsmth} applies with parameter $\nu^{(i)}\sigma_{\min}(A^{(i)})^2$ for each summees. 
    This can't be known if it only satisfies Assumption \ref{ass:sum-of-many}. 
    \par
    The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
    The following assumption state the interpolation hypothesis in our context. 
    \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
        Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
        In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
        \par
        Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$. 
    \end{assumption}

    Due to the fact the algorithms have to be very different support convergence claim for different assumptions on the functions, the following definition gives a generic ideas for all algorithms that specializes on top of it for different assumptions placed on the objective functions. 
    These definitions are not actual algorithms, they are conditions an algorithm must adhere to for the theorems based on it to be valid. 
    Read then as specifications. 
    \begin{definition}[SNAPG-V2 prototype \textcolor{red}{NEW}]\;\label{def:snapg-v2-proto}\\
        Let 
        \begin{enumerate}[nosep]
            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, 
            \item $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$, 
            \item $\sigma^{(k)}$ be another list of i.i.d random variable. 
            \item $\tilde \mu \ge 0$ be a constant that is fixed.
            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 
        \end{enumerate}
        Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
        The SNAPG prototype specifies algorithm that generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
            & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \sigma^{(k)}\right)^{-1}, \\
            & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\

>>>>

% ==============================================================================
\section{Introduction}
    Does stochastic accelerated Nesterov's acceleration (SNAG) produces accelerated convergence rate (or, any type of convergence) when the Interpolation Hypothesis is true? 
    \cite{bauschke_convex_2017}
    Previously we got some results, but unfortunately it was incorrect the mistake is diffcult to recover. 
    \par
    \textbf{However, I don't think that it's true after some mistakes from previous version of the notes and careful investigations.}
    In this file we develop some sufficient conditions for Linear convergence of (SNAG). 
    We will give explanations on why we don't think this is necessarily true.

@@

    Unless specifically specified in the context, we use the following notations. 
    $\Pi_C$ denotes the projection onto a set $C$. 
    Let $A \in \RR^{m \times n}$ be a matrix. 
    $\sigma_{\min}(A)$ denotes the smallest non-zero absolute value of all singular values of $A$. 
    Let $\Vert A\Vert$ denotes the spectral norm of the matrix $A$. 
    $I$ denotes the identity operator. 
    When two expressions are connected via non-trivial results, it's expressed with $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ where $(\cdot)$ is a label of some intermediate results immediately before it, or explained right after a chain of expressions. 

@@

            We note that usually the Bregman Divergence is used with a Legendre function, but in here, we do not assume that $f$ has to be Legendre. 

@@

        \begin{definition}[Lipschitz smoothness and strongly convex]\label{def:lip-smooth-and-scnvx}
            A differentiable function $f: \RR^n \rightarrow \RR$ is $L$ lipschitz smooth and, $\mu$ strong convex for some $L > \mu \ge 0$ if and only if for all $x, y \in \RR^n$ it satisfies the inequality 

@@

                \frac{\mu}{2}\Vert x - y\Vert^2 \le D_f(x, y) \le \frac{L}{2}\Vert x - y\Vert^2. 

@@

@@

    \subsection{important inequalities}
        \begin{assumption}\label{ass:smooth-plus-nonsmooth}
            Suppose that $F = f + g$ where $f, g$ are both convex, proper and closed. 
            In addition, assume $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex satisfying Definition \ref{def:lip-smooth-and-scnvx}. 

@@

@@

        \begin{lemma}[inexact proximal gradient inequality]\label{lemma:inex-pg-ineq}
            Let $F = f + g$ satisfies Definition \ref{def:lip-smooth-and-scnvx} with $L > \mu \ge 0$. 
            Let $x \in \RR^n$ be fixed. 
            Suppose an inexact evaluation of proximal gradient operator at $x$ yield an approximation $\tilde x$, characterized by: 

@@

                & D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2, 
                & \exists: w \in \partial \left[
                    z \mapsto  g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
                \right](\tilde x)\; \text{s.t: } \Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert. 

@@

            Then, it would satisfy for all $z\in \RR^n$ the inequality: 
                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 

@@

            Let $h = z \mapsto g(z) + \langle \nabla f(x), z - x\rangle + B/2\Vert z - x\Vert^2$. 
            $h$ is a $B$ strongly convex function, using the subgradient inequality of a strongly convex function it has for all $z \in \RR^n$: 

@@

                \frac{B}{2}\Vert z - \tilde x\Vert^2
                &\le h(z) - h(\tilde x) - \langle w, z - \tilde x\rangle

@@

                    g(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
                        g(\tilde x) + \langle \nabla f(x), \tilde x - x\rangle + \frac{B}{2}\Vert \tilde x - x\Vert^2
                    - \langle w, z - \tilde x\rangle

@@

                    g(z) + f(z) - f(z) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert z - x\Vert^2
                        g(\tilde x) + f(\tilde x) - f(\tilde x) 
                        + \langle \nabla f(x), \tilde x - x\rangle + \frac{B}{2}\Vert \tilde x - x\Vert^2
                    - \langle w, z - \tilde x\rangle
                    F(z) - D_f(z, x) + \frac{B}{2}\Vert z - x\Vert^2
                        F(\tilde x) - D_f(\tilde x, x) + \frac{B}{2}\Vert \tilde x - x\Vert^2
                    - \langle w, z - \tilde x\rangle
                &\underset{\text{(a)}}{\le} F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 - \langle w, z - \tilde x \rangle
                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2 - 0 + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert. 

@@

            At (a), we used the fact that $f$ is $L > \mu \ge 0$ Lipschitz smooth and strongly convex therefore it has for all $y \in \RR^n$: 

@@

                0 
                \le \frac{L}{2}\Vert z - y\Vert^2  - D_f(z, y)
                \le \frac{L - \mu}{2}\Vert z - y\Vert^2. 

@@

            At (b) we used the Cauchy Inequality and, the assumption $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert$. 
            Continuing it has 

@@

                F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
                + \epsilon \Vert x - \tilde x\Vert\Vert z - \tilde x\Vert 
                - \frac{B}{2}\Vert z - \tilde x\Vert^2

@@

                    - \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2
                    + \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 + \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2

@@

                &= F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
                - \frac{1}{2}\left(
                    \sqrt{\epsilon}\Vert z - \tilde x\Vert - \sqrt{\epsilon}\Vert x - \tilde x\Vert
                - \frac{B}{2}\Vert z - \tilde x\Vert^2

@@

                    &\quad 
                    + \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2 + \frac{\epsilon}{2}\Vert z - \tilde x \Vert^2

@@

                &= F(z) - F(\tilde x) + \frac{\max(B, L) - \mu}{2}\Vert z - x\Vert^2
                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2. 

@@

            Usually in practice, the precise value of $F(\tilde x)$ is never known, therefore, $B$ cannot be easily determined via $D_f(\tilde x, x)$. 
            Hence, in this case we can only choose $B \ge L$ which gives: 
                F(z) - F(\tilde x) + \frac{L - \mu}{2}\Vert z - x\Vert^2
                - \frac{B - \epsilon}{2}\Vert z - \tilde x\Vert^2
                + \frac{\epsilon}{2}\Vert x - \tilde x \Vert^2.

@@

        Note, an inexact evaluation of the proximal gradient operator can be caused by an inexact gradient on the smooth part. 
        Suppose that one take $\tilde \nabla f(x)$ to be an estimate of $\nabla f(x)$ and use it for the proximal gradient operator to produce $\tilde x$, then: 

@@

            \mathbf 0 
            &\in \partial g(\tilde x) + \tilde \nabla f(x) + B(\tilde x - x)
